### 2017-03-02 Lab_4/solutions/L4-1-1.tex

5 broadcast beacon frame

2528 probe 
2529 probe reply
2694 association request van sta1 naar ap waar ssid in staat

>>>>

\begin{itemize}
\item PacketID example 5   , Beacon frame broadcast by the AP (or distributed amongst stations in an IBSS network) contains the SSID, in this case, wmn-1-A.
\item PacketID example 2528, Probe Request, in case of directed probe request contains the SSID of the network the station wants more information about. The other case is when no SSID is specified and "Broadcast" is used as SSID, in that case no SSID name is visible in this packet.
\item PacketID example 2529, Probe Response, response from AP containing capability information, supported data rates, etc., sent after receiving a probe request. The SSID is listed under tagged parameters and is equal to wmn-1-A.
\item PacketID example 2694, Association Request, part of the process where a station registers and connects to an AP. This first step contains the SSID with which the STA wants to connect and is sent to the corresponding AP.
\end{itemize}

### 2017-03-02 Lab_4/solutions/L4-1-2.tex

278: broadcasted probe request for the ssid wmn-1-A sent by STA1
279: the answer is from AP to STA1 and contains the ssid as well

in the association request <pkt id> the ssid is still listed. 
further communication such as association requests also contain the ssid

only broadcasts are now gone such as pkt 5 in the first L411

-- only authentication seen

>>>>

The SSID itself can still be seen in following packet / frame types, despite SSID hiding:
\begin{itemize}
\item PacketID 455  , Probe Request
\item PacketID 456  , Probe Response
\item PacketID 617  , Association Request
\end{itemize}
The beacon frames sent by our AP can no longer be used to determine the SSID but other traffic still works.
With the parameter being "ignore_broadcast_ssid", it was to be expected only the beacon frames would no longer contain the SSID.
